### 2024-03-22 content/chapter_2.tex
:pencil: Add WPT modules and harvester behavior

	\begin{subsection}{Wave Scattering Models}
		\begin{subsection}{Principles}
			\label{sc:principles}
			\gls{rf} wave can be manipulated by scattering elements made from \emph{programmable metamaterials} or \emph{passive antennas} \cite{Liang2022}.
			As discussed above, the former refracts or reflects the incident signals at the air-cell boundary and mainly applies a phase shift.
			In contrast, the latter allows the wave to feed into and collect from the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
			An interesting observation is that when excited by an external wave, a scattering element can simultaneously function as an object and a radiator.
			The corresponding scattered field is \cite{Hansen1989}
			\begin{equation}
				\vec{E}_\text{scatter}(Z_\mathrm{L}) = \underbrace{\vec{E}_\text{structural}}_\text{structural component} + \underbrace{\Gamma I_\mathrm{M} \vec{E}_\text{antenna}}_\text{antenna component},
			\end{equation}
			where $Z_\mathrm{L}$ is the load impedance, $\vec{E}_\text{structural}$ is the residual field under perfect matching (i.e., modelling as an object), $\vec{E}_\text{antenna}$ is the radiated field with unit current at the terminal and no external excitation (i.e., modelling as a radiator), $I_\mathrm{M}$ is the current under perfect matching, and $\Gamma$ is the reflection coefficient
			\begin{equation}
				\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0},
				\label{eq:reflection_coefficient}
			\end{equation}
			and $Z_0$ is the characteristic impedance for programmable metamaterials or the input impedance for passive antennas.
			It is worth mentioning that
			\begin{itemize}
				\item \emph{Structural component:} Depends on the geometry and material of the scatterer. It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or simply regarded a \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
				\item \emph{Antenna component:} Depends on the reflection coefficient that can be altered by load impedance. This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2022a}.
			\end{itemize}
			We then introduce two canonical \gls{ris} models that will be adopted in the work chapters.
			More accurate models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and measurement fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature.
			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
		\end{subsection}

		\begin{subsection}{Diagonal Phase Shift Model}
			A straightforward way to model the \gls{ris} scattering effect is to consider independent scattering elements with purely reactive load impedance \cite{Wu2018}.
			The reflection coefficient of the $n$-th element is thus
			\begin{equation}
				\theta_n = \frac{\jmath X_n - Z^*}{\jmath X_n + Z} = \exp(\jmath \phi_n),
			\end{equation}
			where $X_n$ is the reactance and $\phi_n$ is the phase shift on the scattered wave.
			For a total of $N_\mathrm{S}$ elements, the \gls{ris} scattering matrix is \emph{diagonal with complex unit-magnitude entries}
			\begin{equation}
				\mathbf{\Theta} = \mathrm{diag}(\theta_1, \ldots, \theta_{N_\mathrm{S}}) =
				\begin{bmatrix}
					\theta_1 & 0 & \cdots & 0 \\
					0 & \theta_2 & \cdots & 0 \\
					\vdots & \vdots & \ddots & \vdots \\
					0 & 0 & \cdots & \theta_{N_\mathrm{S}}
				\end{bmatrix}.
			\end{equation}
			Despite the strong assumptions, this diagonal phase shift model is widely used for the analysis of \gls{ris} systems due to its simplicity and analytical tractability.
		\end{subsection}

		\begin{subsection}{\glsfmtfull{bd} Model}
			How to model the \gls{ris} response if the passive scattering elements can be cooperative instead of independent?
			This question has been answered by \cite{Shen2020a} where a \gls{bd} model was proposed.
			From a network theory perspective \cite{Ivrlac2010}, the interaction between the scattering elements can be modelled as lossless (but not necessarily symmetric) in-group connections in an $N_\mathrm{S}$-port circuit network, as shown in Figs. \ref{fg:bd_ris_architecture_1} and \ref{fg:bd_ris_architecture_2} \cite{Shen2020a}.
			This architecture allows wave impinging on any element to propagate within the circuit and depart partially from other elements in the same group.
			\begin{figure}[H]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\includegraphics{assets/chapter_2/bd_ris_architecture_1.eps}
				}
				\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. The figure is from \cite{Shen2020a}.}
				\label{fg:bd_ris_architecture_1}
			\end{figure}
			\begin{figure}[H]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\includegraphics{assets/chapter_2/bd_ris_architecture_2.eps}
				}
				\caption{Network model of an 8-element \gls{ris} with group-wise cooperative scattering of group size (a) 2 and (b) 4. The group size is a design parameter to balance the circuit complexity and scattering performance. The figure is from \cite{Shen2020a}.}
				\label{fg:bd_ris_architecture_2}
			\end{figure}

@@

			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2023a}.
			One element is in the same group with another if and only if there is at least one path (via edges) between them.
			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
		\end{subsection}
	\end{subsection}
\end{section}

@@

		Radiative \gls{wpt}\footnote{In the following part of the thesis, \gls{wpt} refers to radiative \gls{wpt}.} brings numerous opportunities to future wireless networks.
		First, it completely eliminates wired connections and can be integrated into existing wireless systems with minimum modifications.
		Those properties translate to simple deployment, high scalability, and low maintenance cost.
		Second, the power can be simultaneously radiated to multiple devices on demand in a predictable, sustainable and reliable manner.
		This supports our initial vision and is different from other uncontrollable and intermittent energy sources.
		Third and most importantly, radio waves carries power and information simultaneously such that \gls{wpt} can be jointly designed with \gls{wit} to make the most of radiation, spectrum and infrastructures.
		However, energy efficiency and safety concerns have been two major obstacles that limit the practical development of \gls{wpt}.
		We will discuss how \gls{ris} can help address these issues in Section \ref{sc:swipt}
	\end{subsection}

	\begin{subsection}{Modules and Coupling Effect}
		\begin{subsubsection}{Block Diagram}

		\end{subsubsection}

		\begin{subsubsection}{Blockwise Coupling}

		\end{subsubsection}
	\end{subsection}

	\begin{subsection}{Non-Linear Harvester Behavior}
		\begin{subsubsection}{Rectifier Circuits}

		\end{subsubsection}

@@

		\end{subsubsection}

		\begin{subsubsection}{Impact on Waveform Selection}

		\end{subsubsection}
	\end{subsection}
\end{section}

>>>>

	\begin{subsection}{Wave Scattering Models}
		\begin{subsubsection}{Principles}
			\label{sc:principles}
			\gls{rf} wave can be manipulated by scattering elements made from \emph{programmable metamaterials} or \emph{passive antennas} \cite{Liang2022}.
			As discussed above, the former refracts or reflects the incident signals at the air-cell boundary and mainly applies a phase shift.
			In contrast, the latter allows the wave to feed into and collect from the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
			An interesting observation is that when excited by an external wave, a scattering element can simultaneously function as an object and a radiator.
			The corresponding scattered field is \cite{Hansen1989}
			\begin{equation}
				\vec{E}_\text{scatter}(Z_\mathrm{L}) = \underbrace{\vec{E}_\text{structural}}_\text{structural component} + \underbrace{\Gamma I_\mathrm{M} \vec{E}_\text{antenna}}_\text{antenna component},
			\end{equation}
			where $Z_\mathrm{L}$ is the load impedance, $\vec{E}_\text{structural}$ is the residual field under perfect matching (i.e., modelling as an object), $\vec{E}_\text{antenna}$ is the radiated field with unit current at the terminal and no external excitation (i.e., modelling as a radiator), $I_\mathrm{M}$ is the current under perfect matching, and $\Gamma$ is the reflection coefficient
			\begin{equation}
				\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0},
				\label{eq:reflection_coefficient}
			\end{equation}
			and $Z_0$ is the characteristic impedance for programmable metamaterials or the input impedance for passive antennas.
			It is worth mentioning that
			\begin{itemize}
				\item \emph{Structural component:} Depends on the geometry and material of the scatterer. It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or simply regarded a \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
				\item \emph{Antenna component:} Depends on the reflection coefficient that can be altered by load impedance. This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2022a}.
			\end{itemize}
			We then introduce two canonical \gls{ris} models that will be adopted in the work chapters.
			More accurate models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and measurement fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature.
			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
		\end{subsubsection}

		\begin{subsubsection}{Diagonal Phase Shift Model}
			A straightforward way to model the \gls{ris} scattering effect is to consider independent scattering elements with purely reactive load impedance \cite{Wu2018}.
			The reflection coefficient of the $n$-th element is thus
			\begin{equation}
				\theta_n = \frac{\jmath X_n - Z^*}{\jmath X_n + Z} = \exp(\jmath \phi_n),
			\end{equation}
			where $X_n$ is the reactance and $\phi_n$ is the phase shift on the scattered wave.
			For a total of $N_\mathrm{S}$ elements, the \gls{ris} scattering matrix is \emph{diagonal with complex unit-magnitude entries}
			\begin{equation}
				\mathbf{\Theta} = \mathrm{diag}(\theta_1, \ldots, \theta_{N_\mathrm{S}}) =
				\begin{bmatrix}
					\theta_1 & 0 & \cdots & 0 \\
					0 & \theta_2 & \cdots & 0 \\
					\vdots & \vdots & \ddots & \vdots \\
					0 & 0 & \cdots & \theta_{N_\mathrm{S}}
				\end{bmatrix}.
			\end{equation}
			Despite the strong assumptions, this diagonal phase shift model is widely used for the analysis of \gls{ris} systems due to its simplicity and analytical tractability.
		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{bd} Model}
			How to model the \gls{ris} response if the passive scattering elements can be cooperative instead of independent?
			This question has been answered by \cite{Shen2020a} where a \gls{bd} model was proposed.
			From a network theory perspective \cite{Ivrlac2010}, the interaction between the scattering elements can be modelled as lossless (but not necessarily symmetric) in-group connections in an $N_\mathrm{S}$-port circuit network, as shown in Figs. \ref{fg:bd_ris_architecture_1} and \ref{fg:bd_ris_architecture_2} \cite{Shen2020a}.
			This architecture allows wave impinging on any element to propagate within the circuit and depart partially from other elements in the same group.
			\begin{figure}[H]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\includegraphics{assets/chapter_2/bd_ris_architecture_1.eps}
				}
				\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. The figure is from \cite{Shen2020a}.}
				\label{fg:bd_ris_architecture_1}
			\end{figure}
			\begin{figure}[H]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\includegraphics{assets/chapter_2/bd_ris_architecture_2.eps}
				}
				\caption{Network model of an 8-element \gls{ris} with group-wise cooperative scattering of group size (a) 2 and (b) 4. The group size is a design parameter to balance the circuit complexity and scattering performance. The figure is from \cite{Shen2020a}.}
				\label{fg:bd_ris_architecture_2}
			\end{figure}

@@

			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2023a}.
			One element is in the same group with another if and only if there is at least one path (via edges) between them.
			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
		\end{subsubsection}
	\end{subsection}
\end{section}

@@

		Radiative \gls{wpt}\footnote{In the following part of the thesis, \gls{wpt} refers to radiative \gls{wpt}.} brings numerous opportunities to future wireless networks.
		First, it completely eliminates wired connections and can be integrated into existing wireless systems with minimum modifications.
		Those properties translate to simple deployment, high scalability, and low maintenance cost.
		Second, the power can be simultaneously radiated to multiple devices on demand in a predictable, sustainable and reliable manner.
		This supports our initial vision and is different from other uncontrollable and intermittent energy sources.
		Third and most importantly, radio waves carries power and information simultaneously.
		\gls{wpt} can therefore be jointly designed with \gls{wit} to make the most of radiation, spectrum and infrastructures.
		However, energy efficiency and safety concerns have been two major obstacles that limit the practical development of \gls{wpt}.
		In Section \ref{sc:swipt}, we will discuss how \gls{ris} can help address these issues.
	\end{subsection}

	\begin{subsection}{Modules and Coupling Effect}
		\begin{figure}[H]
			\centering
			\resizebox{\columnwidth}{!}{
				\input{assets/chapter_2/wpt_architecture.tex}
			}
			\caption{Block diagram of a closed-loop \gls{ris}-aided \gls{wpt}.}
			\label{fg:wpt_architecture}
		\end{figure}

		The block diagram a closed-loop \gls{ris}-aided \gls{wpt} system is illustrated in Fig. \ref{fg:wpt_architecture}.
		The \gls{rf} signal is generated and radiated by the energy transmitter, propagated through a wireless channel in the presence of a \gls{ris}, captured by the antenna(s) at the receiver, converted to \gls{dc} power by rectifier(s), then passed to the power management unit.
		Upon successful harvesting, the \gls{dc} power is either delivered directly to the device or stored in a battery/super capacitor for future operations.
		When a feedback link is available, one can acquire \gls{csi} at the energy transmitter and exploit it for signal optimization.
		Such a closed-loop \gls{ris}-aided \gls{wpt} system can provide a complete control of transmitter, channel, and receiver, which is essential for maximizing the end-to-end power transfer efficiency
		\begin{equation}
			\eta = \frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{T}} = \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{T}}{P_{\mathrm{DC}}^\mathrm{T}}}_{\eta_1} \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{T}}}_{\eta_2} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{R}}}_{\eta_3} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{R}}}_{\eta_4},
		\end{equation}
		where $P_{\mathrm{DC}}^\mathrm{T}$ is the transmitted \gls{dc} power, $P_{\mathrm{RF}}^\mathrm{T}$ is the transmitted \gls{rf} power, $P_{\mathrm{RF}}^\mathrm{R}$ is the received \gls{rf} power, $P_{\mathrm{DC}}^\mathrm{R}$ is the received \gls{dc} power, and $P_{\mathrm{DC}}^\mathrm{S}$ is the stored \gls{dc} power.
		The power conversion efficiencies are specified below:
		\begin{itemize}
			\item $\eta_1$: Transmitter \gls{dc}-to-\gls{rf} conversion efficiency\footnote{This is different from \gls{pae} used in amplifier rating, which takes into account both \gls{dc} power and input waveform power \cite{Joung2015}.} that depends on the \gls{rf} power amplifier and transmit antenna. It is also called ``drain efficiency'' and state-of-the-art designs can achieve $\eta_1 \ge 70\%$ \cite{Alizadeh2020}.
			\item $\eta_2$: Channel \gls{rf}-to-\gls{rf} conversion efficiency that depends on the wireless environment and \gls{ris} configuration. This is the major bottleneck of \gls{wpt} since the radiated power is inversely proportional to the propagation distance squared.
			\item $\eta_3$: Receiver \gls{rf}-to-\gls{dc} conversion efficiency that depends on the impedance matching and rectifier design. We will discuss its behavior and modelling in the next subsection.
			\item $\eta_4$: Storage \gls{dc}-to-\gls{dc} conversion efficiency that depends on the converter circuit and battery characteristics. Modern power management units can achieve a charging efficiency $\eta_4 \ge 90\%$ \cite{Tan2012}.
		\end{itemize}
		It is worth mentioning that $\eta_1$ and $\eta_3$ also depend on the characteristics of input waveform like power level, carrier frequency, and \gls{papr} \cite{Clerckx2016a}.
		Extensive efforts have been contributed from \gls{rf}, wireless communications, and power electronic communities to improve the conversion efficiency of individual modules.
		However, it is often overlooked in the literature that a practical \gls{wpt} system is highly \emph{non-linear} since the amplifier and rectifier are very sensitive to the input waveform.
		This non-linear behavior can lead to a \emph{coupling effect} between the modules, such that optimizing $\eta_1$ to $\eta_4$ independently does not necessarily maximize the end-to-end power efficiency $\eta$ \cite{Clerckx2016a}.
		Besides, the system modeling and analysis are subject to practical constraints like diode threshold and reverse-breakdown voltages, device parasitics, impedance mismatch, and harmonic generation  \citep{Valenta2014}.
	\end{subsection}

	\begin{subsection}{Non-Linear Harvester Behavior}
		\begin{subsubsection}{Equivalent Circuits}
			\begin{figure}[H]
				\centering
				\subfloat[Rectenna]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/rectenna.tex}
					}
					\label{fg:rectenna}
				}
				\subfloat[Half-wave rectifier]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/halfwave_rectifier.tex}
					}
					\label{fg:halfwave_rectifier}
				}
				\caption{
					Equivalent circuit of (a) rectenna and (b) single-diode half-wave rectifier.
				}
				\label{fg:harvester_circuit}
			\end{figure}
			The rectifier is a nonlinear circuit that converts the \gls{rf} signal to \gls{dc} power by rectifying and filtering the input signal.
			Figs. \ref{fg:harvester_circuit} illustrates the equivalent circuits of a rectenna (antenna and rectifier) and a single-diode half-wave rectifier, where $v_{\mathrm{S}}$ is the source voltage on the receive antenna, $Z_{\mathrm{A}} = R_{\mathrm{A}} + \jmath X_{\mathrm{A}}$ is the antenna impedance, $Z_{\mathrm{in}} = R_{\mathrm{in}} + \jmath X_{\mathrm{in}}$ is the total impedance of the matching network and rectifier, $v_{\mathrm{in}}$ is input voltage on the matching network and rectifier, $v_{\mathrm{D}}$ is the diode voltage, $C$ is the buffer capacitance, $R_{\mathrm{L}}$ is the rectifier load resistance, and $v_{\mathrm{out}}$ is the output voltage.
			It is worth mentioning that the half-wave rectifier is the most popular choice in \gls{wpt} literature due to its simple behavior and low cost.
			Other rectifier topologies like full-wave, bridge, and voltage doubler can potentially improve the \gls{rf}-to-\gls{dc} conversion efficiency \cite{Rotenberg2020}, but their modeling and analysis are much more complicated.
		\end{subsubsection}

@@

			The diode is the key non-linear component that determines to the harvested energy.
			Generally speaking, the behavior of any rectenna can be separated into three operation regions \cite{Clerckx2016a}:
			\begin{itemize}
				\item \emph{Linear region:} When the input power level is relatively low, the output power is proportional to the input and the \gls{rf}-to-\gls{dc} conversion efficiency $\eta_3$ is a constant. Most early \gls{wpt} research (especially from communications society) assume the rectenna works in this region. For a received signal $y(t)$, the harvested \gls{dc} power in this region can be modelled as
				\begin{equation}
					P_\mathrm{DC}^\mathrm{R} = \eta_3 P_\mathrm{RF}^\mathrm{R} = \eta_3 \mathbb{E}\bigl\{ \lvert y(t) \rvert^2 \bigr\},
					\label{eq:dc_power_linear}
				\end{equation}
				which suggests that maximizing the received \gls{rf} signal power is sufficient to maximize the harvested \gls{dc} power.
				\item \emph{Non-linear (transition) region:} When the input power level is moderate, the output power increases \emph{exponentially} with the input and $\eta_3$ is significantly higher than the linear region. This is the most interesting region that can be exploited to improve the overall power efficiency.
				For a tractable model, consider a perfectly matched ($Z_\mathrm{in} = Z_\mathrm{A}^*$) half-wave rectifier in Fig.~\subref*{fg:halfwave_rectifier} and assume the voltage across the matching network is negligible. The received \gls{rf} power is totally transferred to the rectifier input $P_\mathrm{RF}^\mathrm{R} = \mathbb{E}\bigl\{ \lvert y(t) \rvert^2 \bigr\} = \mathbb{E}\bigl\{ \lvert v_\mathrm{in}(t) \rvert^2 / R_\mathrm{in} \bigr\} = \mathbb{E}\bigl\{ \lvert v_\mathrm{in}(t) \rvert^2 / R_\mathrm{A} \bigr\}$ such that the voltage sources can be expressed in terms of the received signal \cite{Clerckx2016a}
				\begin{equation}
					v_\mathrm{in}(t) = y(t) \sqrt{R_\mathrm{A}}, \quad v_\mathrm{S}(t) = 2 y(t) \sqrt{R_\mathrm{A}}.
				\end{equation}
				The current passing through the diode is given by the characteristic equation $i_\mathrm{D}(t) = I_\mathrm{S} \bigl( \exp(v_\mathrm{D}(t) / n v_\mathrm{T}) - 1 \bigr)$, where $I_\mathrm{S}$ is the reverse bias saturation current, $v_\mathrm{T}$ is the thermal voltage, and $n$ is the ideality factor. Its Taylor expansion around the steady point $-v_\mathrm{out}$ is \cite{Clerckx2016a}
				\begin{equation}
					i_\mathrm{D}(t) = \sum_{i=0}^\infty k_i \bigl(v_\mathrm{D}(t)+v_\mathrm{out}\bigr)^i = \sum_{i=0}^\infty k_i v_\mathrm{in}^i(t) = \sum_{i=0}^\infty k_i R_\mathrm{A}^{i/2} y^i(t),
				\end{equation}
				where $k_0 = I_\mathrm{S} \bigl(\exp(-{v_\mathrm{out}}/{n v_\mathrm{T}})-1\bigr)$, $k_i = I_\mathrm{S} \frac{\exp(-v_\mathrm{out}/n v_\mathrm{T})}{i!(n v_\mathrm{T})^i}$ for $k \in \mathbb{N}$.
				The rectifier output \gls{dc} current can be written as a function of the received signal
				\begin{equation}
					i_\mathrm{out} = \sum_{i=0}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{E}\bigl\{ y^i(t) \bigr\} = \sum_{i=0,\text{even}}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{E}\bigl\{ y^i(t) \bigr\}
					\label{eq:dc_current_expansion}
				\end{equation}
				where the second equality is because $\mathbb{E}\bigl\{y^i(t)\bigr\} = 0$ for odd $i$. Note that the dependency of $k_i$ on $-v_\mathrm{out}=-i_\mathrm{out} R_\mathrm{L}$ makes it nontrivial to formulate a closed-form expression for the harvested \gls{dc} power.
				Fortunately, it is shown in \cite{Clerckx2016a} that maximizing the harvested \gls{dc} power is equivalent to maximizing the quantity
				\begin{equation}
					z = \sum_{i=2,\text{even}}^\infty \beta_i \mathbb{E}\bigl\{ y^i(t) \bigr\},
					\label{eq:dc_power_nonlinear}
				\end{equation}
				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant. Truncating \eqref{eq:dc_power_nonlinear} at the second order yields the same result as \eqref{eq:dc_power_linear}, which suggests that the linear model is a special case of the more accurate non-linear model. For a moderate excitation, the contribution of higher-order terms is significant and should be modelled in the harvested \gls{dc} power.
				\item \emph{Saturation region:} When the input power level is too high, the diode works in the reverse breakdown region, the rectifier is saturated, and the output power is a constant. This is the region where the $\eta_3$ significantly drops and should be avoided by circuit design.
				For a fixed rectenna with Gaussian input signal, a parametric model was proposed in \cite{Boshkovska2015}
				\begin{equation}
					P_{\mathrm{DC}}^\mathrm{R} = \frac{\Psi_{\mathrm{DC}}-P_{\text{sat}}\Omega}{1-\Omega}, \quad \Psi_{\mathrm{DC}} = \frac{P_{\text{sat}}}{1+\exp\bigl(-a(P_{\mathrm{RF}}^\mathrm{R}-b)\bigr)}, \quad \Omega = \frac{1}{1 + \exp(ab)},
					\label{eq:saturation_model}
				\end{equation}
				where the constant $P_{\text{sat}}$ denotes the maximum harvested power when the rectifier is saturated, and the constants $a$ and $b$ model the nonlinear charging rate with respect to input power and the minimum turn-on voltage of the rectifier, respectively.
				Parameters $P_{\text{sat}}$, $a$, and $b$ can be obtained by curve fitting over measurement results.
			\end{itemize}

			The exact boundaries between those regions depend on the rectifier circuit and input waveform \citep{Zeng2017}.
			Signals with a higher \gls{papr} usually exhibit the nonlinear and saturation effects at lower input power levels.
			For example, the nonlinear region is typically $[-20,0]$ dBm for a \gls{cw} and $[-30,-10]$ dBm for a multisine \citep{DelPrete2016}.
			This not only motivates adaptive multi-carrier waveform designs \cite{Clerckx2016a,Zeng2017,Huang2017,Shen2021} but also calls for a joint optimization of the transmitter, channel (via \gls{ris}), and receiver to improve the end-to-end power efficiency.
		\end{subsubsection}
	\end{subsection}
\end{section}

### 2024-03-22 misc/glossaries.tex
:pencil: Add wave scattering models
:pencil: Add WPT introduction
:pencil: Add WPT modules and harvester behavior

@@

@@

@@

\nomenclature[n-1]{$\mathbb{R}$}{Real numbers}
\nomenclature[n-2]{$\mathbb{R}_+$}{Real nonnegative numbers}
\nomenclature[n-3]{$\mathbb{C}$}{Complex numbers}
\nomenclature[n-4]{$\mathbb{I}$}{Probability domain $[0,1]$}
\nomenclature[n-5]{$\mathbb{H}_+^{n \times n}$}{Positive semi-definite matrices of dimension $n \times n$}
\nomenclature[n-6]{$\mathbb{U}^{n \times n}$}{Unitary matrices of dimension $n \times n$}

\nomenclature[c-j]{$\jmath$}{The imaginary unit $= \sqrt{-1}$}
\nomenclature[c-e]{$e$}{Euler's number $\simeq 2.71828\ldots$}
\nomenclature[c-pi]{$\pi$}{Archimedes' constant $\simeq 3.14159\ldots$}

>>>>

\newacronym{star}{STAR}{Simultaneous Transmission and Reflection}

@@

\newacronym{wsn}{WSN}{Wireless Sensor Network}

@@

\newacronym{ble}{BLE}{Bluetooth Low Energy}
\newacronym{lorawan}{LoRaWAN}{Long Range Wide Area Network}
\newacronym{pae}{PAE}{Power-Added Efficiency}
\newacronym{papr}{PAPR}{Peak-to-Average Power Ratio}

@@

\nomenclature[n-1]{$\mathbb{N}$}{Natural numbers (excluding 0)}
\nomenclature[n-2]{$\mathbb{R}$}{Real numbers}
\nomenclature[n-3]{$\mathbb{R}_+$}{Real nonnegative numbers}
\nomenclature[n-4]{$\mathbb{C}$}{Complex numbers}
\nomenclature[n-5]{$\mathbb{I}$}{Probability domain $[0,1]$}
\nomenclature[n-6]{$\mathbb{H}_+^{n \times n}$}{Positive semi-definite matrices of dimension $n \times n$}
\nomenclature[n-7]{$\mathbb{U}^{n \times n}$}{Unitary matrices of dimension $n \times n$}

\nomenclature[c-j]{$\jmath$}{Imaginary unit $= \sqrt{-1}$}
\nomenclature[c-e]{$e$}{Euler's number $\simeq 2.71828\ldots$}
\nomenclature[c-pi]{$\pi$}{Archimedes' constant $\simeq 3.14159\ldots$}
